---
title: "Exercise-9"
author: "Mohammad Imtiaz Nur"
date: "4/8/2021"
output: pdf_document
---

# ID : 1878074

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r data_read, include=FALSE}
df_article = read.csv(file = "ArticleLevel-RegData-ALLSA_Xc_1_NData_655386_LONGXCIP2.csv",  header = TRUE)
```

```{r task, warning=FALSE}
library(dplyr)
library(rcompanion)
library(questionr)
library(modelr)     
library(broom)      
library(pscl)

#### Filters
###### Filter Year [1970-2018]
###### Filter Kp >= 2 and Wp >= 2
df_article = df_article %>% filter(Yp >= 1970)
df_article = df_article %>% filter(Yp <= 2018)
df_article = df_article %>% filter(Kp >= 2)
df_article = df_article %>% filter(nMeSHMain >= 2)
df_article = df_article %>% filter(IRegionRefinedp > 0 & IRegionRefinedp < 7)

#### Convert Data types
df_article$eidsp = as.factor(df_article$eidsp)
df_article$Yp = as.integer(df_article$Yp)
df_article$Kp = as.integer(df_article$Kp)
df_article$XCIPp = as.factor(df_article$XCIPp)
df_article$NRegp = as.integer(df_article$NRegp)
df_article$NSAp = as.integer(df_article$NSAp)
df_article$NCIPp = as.integer(df_article$NCIPp)
df_article$nMeSHMain = as.integer(df_article$nMeSHMain)
df_article$IRegionRefinedp = as.factor(df_article$IRegionRefinedp)

## Model 1 - for X_CIP
options(scipen=2)
model1 <- glm(XCIPp ~ Yp + log(Kp) + log(nMeSHMain) + NRegp + NSAp, 
              data = df_article, family=binomial(link='logit'))

# MeanZJp

# Here:
# XCIPp: binary indicator variable = 1 if any 2+ CIP are present, and 0 otherwise
# Yp: article’s publication year
# Kp: article’s coauthor count based upon author list in PubMed record
# NRegp: article’s count variable indicating the total number of regions 
# NSAp: article’s count variable indicating the total number of SAps
```

# Model Summary

```{r summary}
summary(model1)
```

From the above summary, all the p-values of the predictors are very much less than the significance value (0.05). So, all the variables are very much significant for the model for predicting the cross-disciplinary in CIP (XCIPp variable) Classification of Instructional Programs.

# Pseudo r-squared measures

```{r r_squared}
nagelkerke(model1)
```

Our model is compared against the null model. From the McFadden's pseudo r-squared values ranging from 0.2 to 0.4 is a good model fit. The pseudo r-squared values ranges from 0.19 to 0.26 for our model which means though it captures the variance of the data moderately but still not a strong fit.

# Odds ratio

```{r odds_ratio}

output = odds.ratio(model1)
output = apply(output, 2, formatC, format="f", digits=4)
output
```

Odds ratio > 1 means greater likelihood of having the outcome while < 1 refers to lower likelihood of having the outcome.

From the output of the odds ratio, except Major Mesh all the predictors count have odds ratio values greater than 1 which refers to greater likelihood of having the outcome.

The odds ratio for Major Mesh count is less than 1 refers to the likelihood of predicting the outcome is lower by 6.68%.