---
title: "Exercise8"
author: "Mohammad Imtiaz Nur"
date: "4/2/2021"
output: pdf_document
---

# ID: 1878074

# 1.0:

```{r read_data}
data <- read.csv("politeness_data.csv", header = TRUE)
boxplot(frequency~gender*attitude, data = data,
        xlab='pitch',
        ylab='politeness',
        main="Politeness(frequency) vs Pitch(attitude*gender)")
```


In the above plot, for both informal or polite attitudes, male pitching range is lower than female pitching range. 
Also, t is quite clear that there is a difference between female polite and informal frequency. Though the difference in frequency is very low for male, but polite frequency is slightly lower than male informal frequncy.

# 1.1:

```{r model_1}
model_1 <- lm(frequency~attitude, data = data)
summary(model_1)
```

As the p value (0.207) is greater than the significance level (0.05), only attitude variable alone can't make the model significant. Also the R-squared value(0.01958) signifies that our model takes only 1.958% data from the entire dataset which makes the model irrelevant.

# 1.2:

```{r model_2}
model_2 <- lm(frequency~gender, data = data)
summary(model_2)
```


As the p value (< 2.2e-16) is very much lower than the significance level (0.05), the gender variable appears to build a very significant. model. Also the R-squared value(0.6884) signifies that our model takes 68.84% data from the entire dataset which makes the model a good fit for analysis.

# 1.3:

```{r model_3}
model_3 <- lm(frequency~attitude*gender, data = data)
summary(model_3)
```

As the p value (< 2.2e-16) is very much lower than the significance level (0.05), the attitude*gender variables together appears to build a very significant. model. Also the R-squared value(0.7038) signifies that our model takes 70.38% data from the entire dataset which makes the model a good fit for analysis.


# 1.4:

ANOVA test to compare the significance of all three models.

```{r compare}
anova(model_1,model_2)
anova(model_2,model_3)
anova(model_1,model_3)
```


From the ANOVA test, we can summarize that model_3 can be used for more accurate prediction than the other two models.